The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-15 SI.tex
Add parts that deal with 2D - 3D transition

\section{Theoretical Analysis}
\label{sec:theory}
\subsection{Polarizability-Based Theoretical Model}
\label{ssec:theory-1}
In this section we show in detail the polarizability-based theoretical
framework that leads to the 2D Moss-like relations proposed in the
main text.  Due to its highly anisotropic nature, the wavefunction of
an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
in- and out-of-plane components, similar to the treatment of quantum
wells (QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. Next we will show
that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
\ref{main-eq:2D-Moss-perp}.

@@

In this section we show how main text Eq. \ref{main-eq:2D-Moss-para}
is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
$\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent
of $z$, therefore the integral in
$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
becomes the independent of $\psi^{\perp}$, due to the orthogonality
and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
only the cell-function $u(\mathbf{k})$ contributes to the final result
of $\alpha^{\parallel}_{\mathrm{2D}}$ \cite{davies_physics_1997}, such
that:
\begin{equation}
  \label{eq:alpha_para_RPA}
  \alpha_{\mathrm{2D}}^{\parallel} = \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
Present the summation of k-space into integral, and further combining
with the Bloch wave representation and the
$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
at Eq. \ref{main-eq:2D-Moss-para}. Note that from
Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
where $N$ is the degeneracy associated with the minimal bandgap. Such
relation predicts the linear correlation coefficient between
$(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From main
text Figure \ref{main-fig-3}c, we have
$(4 \pi \varepsilon_{0}\cdot \AA{})/\alpha_{\mathrm{2D}}^{\parallel}
\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
between 2 and 3, which is a reasonable result for the 2D materials
studied.

@@

\subsection{}
\label{sec:theory-2}

Eq. 9 is the detailed form of Eq. 6 considering wavefunctions in all
directions are periodic which can be written in the form of Block
waves. The solution for Eq. 9 in main text is derived as follows. For
simplicity we consider that the effective mass $m^{*}$ is uniform,
which is generally a good assumption for bulk materials. Considering
only one pair of valence-conduction transition, and take the result
from \cite{Jiang_2017_Eg_Eb}, we get:
\begin{equation}
  \begin{aligned}
    \label{eq:eps-bulk}
    \varepsilon_{\mathrm{bulk}} - 1 &\propto \int d^{3}\mathbf{k}
    {\displaystyle \frac{1}{(E_{\mathrm{g}} + {\displaystyle
          \frac{\hbar^{2} k^{2}}{m^{*}}})^{2}}}\\
    &= \int_{0}^{k_{\mathrm{BZ}}} {\displaystyle
      \frac{4 \pi k^{2}}{(E_{\mathrm{g}} + {\displaystyle \frac{\hbar^{2}
            k^{2}}{m^{*}}})^{2}}} dk
  \end{aligned}
\end{equation}
where $k_{\mathrm{BZ}}$ is the boundary for the Brillouin Zone. The
last step in Eq. \ref{eq:eps-bulk} assumes the integral within the
Brillouin Zone is equivalent to integral inside a sphere of
k-space. Let $\hbar^{2}/(2 m^{*})=A$, the integral becomes:
\begin{equation}
  \begin{aligned}
    \label{eq:integral-BZ-bulk}
    \varepsilon_{\mathrm{Bulk}} &\propto {\displaystyle \frac{2 \pi
        \mathrm{arctan}(\sqrt{Ak^{2}/E_{\mathrm{g}}})}{\sqrt{E_{\mathrm{g}}A^{3}}}
        - \frac{2\pi k}{A(A+E_{\mathrm{g}}k^{2})}
      } \bigg\rvert_{0}^{k_{\mathrm{BZ}}}\\
      &\propto 1/\sqrt{E_{\mathrm{g}}}
  \end{aligned}
\end{equation}
when $\varepsilon_{\mathrm{Bulk}} \gg 1$. since generally
$\hbar^{2}k_{\mathrm{BZ}}^{2}/(2m^{*}) \gg E_{\mathrm{g}}$. When
$\varepsilon_{\mathrm{bulk}} \gg 1$ \cite{Finkenrath_1988}, it is the
Moss relation of bulk semiconductors.

\subsection{Static 2D polarizability and 2D plasma frequency}
\label{sec:omega-p}

@@

\subsection{Comparing dielectric anisotropy}
The dielectric anisotropy $\eta$ proposed in the main text is also
applied to other dimensions. Similar to the case of 2D and bulk
layered materials, $\epsilon$ is used to compare the anisotropy when
the material is periodic in all dimensions (bulk covalent materials),
while the polarizability $\alpha$ is used for reduced dimensional
materials.

@@

>>>>

\section{Theoretical Analysis}
\label{sec:theory}
\subsection{Polarizability-Based Theoretical Model}
\label{ssec:theory-1}
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by main text
Eqs. \ref{main-eq:2D-Moss-para} and \ref{main-eq:2D-Moss-perp} are not
coincidence. Combining recent theoretical findings of the linear
relation between exciton binding energy $E_{\mathrm{b}}$ and
$E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha_{\mathrm{2D}}^{\parallel}$ \cite{Pulci_2014}, it is reasonable
to have a general Moss-like relation between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}^{-1}$. Moreover,
the bandgap-independent relation of 2D $\alpha_{\mathrm{2D}}^{\perp}$
resembles molecular polarizabilities of conjugate molecules
\cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and carbon
nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.

In this section we show in detail the polarizability-based theoretical
framework that leads to the 2D Moss-like relations proposed in the
main text.  Due to its highly anisotropic nature, the wavefunction of
an isolated 2D material $\psi(\mathbf{r})$ can be separated into the
in- and out-of-plane components, similar to the treatment of quantum
wells (QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)
theory\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ is the
$\mathbf{q} \to 0$ and $\omega \to 0$ limits of the non-interacting
dielectric function $\varepsilon(\mathbf{q}, \omega)$, where
$\mathbf{q}$ is the momentum transfer and $\omega$ is the frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}})\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $E$ is the eigenenergy of individual bands, and $f$ is the
Fermi-Dirac distribution function. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. Next we will show
that the different behavior of $\psi^{\parallel}$ and $\psi^{\perp}$
give rise to the main text Eqs. \ref{main-eq:2D-Moss-para} and
\ref{main-eq:2D-Moss-perp}.

@@

In this section we show how main text Eq. \ref{main-eq:2D-Moss-para}
is derived from Eq. \ref{eq:alpha-RPA}. For the in-plane component
$\alpha_{\mathrm{2D}}^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent
of $z$, therefore the integral in
$|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}$
becomes the independent of $\psi^{\perp}$, due to the orthogonality
and normality. The Bloch-wave form of $\psi^{\parallel}$ ensures that
only the cell-function $u(\mathbf{k})$ contributes to the final result
of $\alpha^{\parallel}_{\mathrm{2D}}$ \cite{davies_physics_1997}, such
that:
\begin{equation}
  \label{eq:alpha_para_RPA}
  \alpha_{\mathrm{2D}}^{\parallel} = \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k} \sum_{\mathrm{c, v}}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(\mathbf{k})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
Present the summation of k-space into integral, and further combining
with the Bloch wave representation and the
$\mathbf{k} \cdot \mathbf{p}$ theory\cite{Jiang_2017_Eg_Eb}, we arrive
at Eq. \ref{main-eq:2D-Moss-para}. Note that from
Ref. \citenum{Jiang_2017_Eg_Eb}, the coefficient between
$\alpha^{\parallel}_{\mathrm{2D}}$ and $E_{\mathrm{g}}$ is given by:
$\alpha_{\mathrm{2D}}^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$,
where $N$ is the degeneracy associated with the minimal bandgap. Such
relation predicts the linear correlation coefficient between
$(4\pi \varepsilon_{0})/\alpha^{\parallel}_{\mathrm{2D}}$ (measured in
\AA{}$^{-1}$) and $E_{\mathrm{g}}$ (measured in eV) as
$8 \pi^{2} \varepsilon_{0} \AA{} / (e N) \approx 0.436 / N$. From main
text Figure \ref{main-fig-3}c, we have
$(4 \pi \varepsilon_{0}\cdot \text{\AA{}})/\alpha_{\mathrm{2D}}^{\parallel}
\sim{} 0.183 E_{\mathrm{g}}/ \mathrm{eV}$, corresponding to $N$
between 2 and 3, which is a reasonable result for the 2D materials
studied.

@@

\subsection{Comparing 2D and 3D Moss relations}
\label{ssec:theory-2}

The 2D Moss-like relation $\alpha^{\parallel} \propto E_{g}^{-1}$ is
similar to the 3D Moss relation $\varepsilon \propto E_{g}^{-1/2}$,
with a different power law. Such difference in the power law can
indeed be explained by modern theory of dielectric properties. From
the 2D material to a bulk covalent semiconductor, the wavefunction
becomes periodic in all directions. Considering only one pair of
valence-conduction transition and uniform effective mass $m^{*}$,
extending the approach Eq. \ref{eq:alpha_perp_RPA} to the bulk
material, and using the Bloch presentation for wavefunctions in all
dimensions, we get \cite{Jiang_2017_Eg_Eb}:
\begin{equation}
  \begin{aligned}
    \label{eq:eps-bulk}
    \varepsilon_{\mathrm{bulk}} - 1 &\propto \int d^{3}\mathbf{k}
    {\displaystyle \frac{1}{(E_{\mathrm{g}} + {\displaystyle
          \frac{\hbar^{2} k^{2}}{m^{*}}})^{2}}}\\
    &= \int_{0}^{k_{\mathrm{BZ}}} {\displaystyle
      \frac{4 \pi k^{2}}{(E_{\mathrm{g}} + {\displaystyle \frac{\hbar^{2}
            k^{2}}{m^{*}}})^{2}}} dk
  \end{aligned}
\end{equation}
where $k_{\mathrm{BZ}}$ is the boundary for the Brillouin Zone. The
last step in Eq. \ref{eq:eps-bulk} assumes the integral within the
Brillouin Zone is equivalent to integral inside a sphere of
k-space. Let $\hbar^{2}/(2 m^{*})=\beta$, the integral becomes:
\begin{equation}
  \begin{aligned}
    \label{eq:integral-BZ-bulk}
    \varepsilon_{\mathrm{Bulk}} &\propto {\displaystyle \frac{2 \pi
        \mathrm{arctan}(\sqrt{\beta k^{2}/E_{\mathrm{g}}})}{\sqrt{E_{\mathrm{g}} \beta^{3}}}
        - \frac{2\pi k}{\beta(\beta +E_{\mathrm{g}}k^{2})}
      } \bigg\rvert_{0}^{k_{\mathrm{BZ}}}\\
      &\propto 1/\sqrt{E_{\mathrm{g}}}
  \end{aligned}
\end{equation}
when $\varepsilon_{\mathrm{Bulk}} \gg 1$. since generally
$\hbar^{2}k_{\mathrm{BZ}}^{2}/(2m^{*}) \gg
E_{\mathrm{g}}$ \cite{Finkenrath_1988}. The final result $\varepsilon_{\mathrm{Bulk}} \propto E_{\mathrm{g}}^{-1/2}$ recovers the original Moss relation for bulk semiconductors.

\subsection{Static 2D polarizability and 2D plasma frequency}
\label{ssec:omega-p}

@@

\subsection{Comparing dielectric anisotropy}
\label{ssec:aniso}
The dielectric anisotropy $\eta$ proposed in the main text is also
applied to other dimensions. Similar to the case of 2D and bulk
layered materials, $\epsilon$ is used to compare the anisotropy when
the material is periodic in all dimensions (bulk covalent materials),
while the polarizability $\alpha$ is used for reduced dimensional
materials.

@@

\subsubsection{Explanation for the separation between 2D and 3D regimes in main text Figure \ref{main-fig:aniso}}
\label{sssec:aniso-1}

### 2018-11-15 paper.tex
Add parts that deal with 2D - 3D transition

\iffalse
  &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
  &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
\fi

@@

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties in
various ways. Using the similar appraoch as we derive the 2D Moss-like
relations, we show that the
$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
relation for a 2D material naturally transforms to
$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
semiconductor, which is the original Moss relation (details see
Supplementary Section SXX \todo{note}). In other words, the proposed
$\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is indeed
the Moss relation in 2D world, while the different power law for
$E_{\mathrm{g}}$ is caused by the electronic confinement.

% As described in the previous section, the 2D Moss-like relation
% between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
% relation between $\varepsilon$ and $E_{g}$, with a different power
% law. Such difference in the power law can indeed be explained by
% modern theory of dielectric properties.  Extend the approach
% Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
% presentation for wavefunctions in all dimensions, we derive (detailed
% procedure see Supplementary Section S4):
% \begin{equation}
  % \label{eq:alpha-Eg-3D}
  % \begin{aligned}[t]
  % \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  % \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  % {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  % &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
% \end{aligned}
% \end{equation}
% which recovers the 3D Moss relation.

@@

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
of corresponding 2D layer (details see Supplementary Section SXX
\todo{note}), which is the basis for the separation of bulk and 2D
regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
we also superimpose the dielectric anisotropy indices $\eta$ of common
semiconducting materials in other dimensions (details see
Supplementary Section S4.5) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}

>>>>

% \begin{subequations}
% \begin{eqnarray}
  % \label{eq:alpha-para-def}
  % &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\
  % \label{eq:alpha-perp-def}
  % &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L
% \end{eqnarray}
% \end{subequations}

@@

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties in
various ways. Using the similar appraoch as we derive the 2D Moss-like
relations, we show that the
$\alpha_{\mathrm{2D}}^{\parallel} \propto E_{\mathrm{g}}^{-1}$
relation for a 2D material naturally transforms to
$\varepsilon \propto E_{\mathrm{g}}^{-\frac{1}{2}}$ for a bulk
semiconductor, which is the original Moss relation (details see
Supplementary Section \ref{SI-ssec:theory-2}). In other words, the
proposed $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation is
indeed the Moss relation in 2D world, while the different power law
for $E_{\mathrm{g}}$ is caused by the electronic confinement.
\todo[inline]{I shortened this paragraph since the derivation is
  interesting but not so much related with other stuff like the
  dielectric anisotropy.}

@@

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
of corresponding 2D layer (details see Supplementary Section SXX
\todo{note}), which is the basis for the separation of bulk and 2D
regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
we also superimpose the dielectric anisotropy indices $\eta$ of common
semiconducting materials in other dimensions (details see
Supplementary Section ) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}
